---
output:
  html_document:
    keep_md: yes
    number_sections: yes
    self_contained: no
    toc: yes
---


```{r message=F, warning=F}
# Imports
library(dplyr)
library(ggplot2)
library(scales)
library(tidyr)
library(readr)
library(lme4)
library(magrittr)
source('Functions.R')

# fig_format = 'svg'
fig_format = 'png'

# Set to F to read values from file, or T to rerun all calculations (takes 20+ minutes)
recalculate_everything = F

# Colours
green = "#4daf4a"
red = "#e41a1c"
blue = "#377eb8"
blue2 = "#37B8B2"
black = '#000000'

data = read_csv('data/long.csv')

## Force charachter columns to factors
i <- sapply(data, is.character)
data[i] <- lapply(data[i], as.factor)

data$subject_nr = factor(data$subject_nr)
levels(data$subject_nr) = 1:length(levels(data$subject_nr))
data$stimuli_number = factor(data$stimuli_number)
data$acc = data$acc == 'True'
data$seconds = data$step / 1000

## Lose the distinction between the two "other" responses
levels(data$choice) = c('correct', 'heuristic', 'other', 'other')
levels(data$section) = c('correct', 'heuristic', 'other', 'other')


# To split the 'bias' measure into groups, I compare people give 3 or 4 heuristic responses,
# to those who give 0, 1, or 2.
b = data %>% group_by(subject_nr) %>% summarise(bias=mean(bias))
# mean(b$bias > .6) # Proportion of subjects who are 'biased'
sum(b$bias==.25) + sum(b$bias==.5) # Number of unbiased reasoners
sum(b$bias>.6) # Number of biased reasoners
data$biased = data$bias > .6

## Currently using every 5th sample (100 msec intervals)
## Change this in preprocess.py as necessary
## Optionally, make the data even sparser here
show_every = 2
if(show_every > 1){
  steps = unique(data$step)
  sparse_steps = steps[seq(1, length(steps), show_every)]
  data = data[data$step %in% sparse_steps,]
}
unique(data$step) %>% head

# Seperate column for each response region status
for(r in c('correct', 'heuristic', 'other')){
  data[[r]] = data$section == r
}

tall.data = data %>%
  select(subject_nr, trial, seconds, choice, condition, stimuli_number, bias, biased,
         correct, heuristic, other) %>%
  gather(section, value, correct, heuristic, other)

# The column 'other' is the sum of fixations on both possible foil responses.
# This is a problem where we want to think about the *probability* of 
# moving towards a foil response, as this combines the probability of going towards either.
# Therefore, for every row corresponding to movement towards a foil,
# I add an extra, identical row to the data, where the foil response
# ISN'T being moved towards.
# Think of this as multiplying to demoninator by 2:
# instead of moving towards either foil on 50/100 trials,
# it's 50/200 trials, so the probability of moving towards a foil response is 25%
filler.data = filter(tall.data, section=='other')
filler.data$value = FALSE

filler.data$is.filler = T # Use this later when excluding these rows
tall.data$is.filler = F

tall.data = rbind(tall.data, filler.data)
tall.data$value = tall.data$value * 1 # Coerces values to 1,0 rather than T,F
tall.data %<>% mutate(to.chosen = section == choice)

# Add orthogonal (ot) and natural (nt) polynomial terms for time to the data
order = 4
ot = poly(tall.data$seconds, order, raw=F) # Orthogonal
nt = poly(tall.data$seconds, order, raw=T) # Natural
for (i in 1:order){
  tall.data[paste("ot", i, sep="")] = ot[,i]
  tall.data[paste("nt", i, sep="")] = nt[,i]
}
scale.to.1 = function(x) x / max(x)
tall.data$ot1 %<>% scale.to.1
tall.data$ot2 %<>% scale.to.1
tall.data$ot3 %<>% scale.to.1

tall.data$nt1 %<>% scale.to.1
tall.data$nt2 %<>% scale.to.1
tall.data$nt3 %<>% scale.to.1

conflict = tall.data[tall.data$condition=='C',]
control = tall.data[tall.data$condition=='B',]

tall.data %<>% mutate(type = interaction(condition, section))
# "B.correct"   "C.correct"   "B.heuristic" "C.heuristic" "B.other"     "C.other"
levels(tall.data$type) = c('Correct no-conflict', 'Correct conflict', 'Foil no-conflict',
						   'Heuristic Conflict', 'Foil no-conflict', 'Foil conflict')
tall.data$type %<>% factor(levels=levels(.)[c(1, 4, 2, 3, 5)])

conflict$Section = conflict$section
levels(conflict$Section) = c('Correct', 'Heuristic', 'Foil')
levels(control$section) = c('Correct', 'Foil', 'Foil')

# Define text sizes for plotting here, and resuse below
my_theme = theme(title = element_text(size = rel(1)),
                 axis.title = element_text(size = rel(1)),
                 axis.text = element_text(size = rel(.9)),
                 legend.title = element_text(size = rel(.9)),
                 legend.text = element_text(size = rel(.9)),
				 legend.background = element_rect(fill=NA))
```

# All responses

Combining both conditions

```{r all.plot, dev=fig_format, fig.width=9, fig.height=5}
g = ggplot(tall.data,
     aes(seconds, value, color=type, alpha=type)) +
	stat_summary(fun.data=mean_se) +
	theme_bw() + 
  scale_color_manual(values=c(blue2, red, green, blue, black)) +
	scale_alpha_manual(values=c(1, 1, 1, .5, .5)) +
	labs(x="Seconds", y="Proportion of trials", colour="Response region", alpha="Response region") + 
	scale_y_continuous(labels=percent) +
	scale_x_continuous(breaks=seq(0, 60, 5)) +
	coord_cartesian(ylim=c(0,.92)) +
	my_theme

g +
  theme(legend.position=c(0,1), legend.justification=c(0,1))
``` 


```{r all.plot.annotate, dev=fig_format, fig.width=9, fig.height=5}
g + 
  annotate('text', x=60, y=.83, label='Correct no-conflict',
           color=blue2, size=6, hjust=1) +
  annotate('text', x=60, y=.645, label='Heuristic conflict',
           color=red, size=6, hjust=1) +
  annotate('text', x=60, y=.39, label='Correct conflict',
           color=green, size=6, hjust=1) +
  annotate('text', x=60, y=.115, label='Foil no-conflict',
           color=blue, size=6, hjust=1) +
  annotate('text', x=60, y=0, label='Foil conflict',
           color=black, size=6, hjust=1) +
  theme(legend.position="none")
```

The following plots show the same data, but separately for conflict and no-conflict conditions.
These are not included in the paper.

## All responses, conflict

```{r all.conflict, dev=fig_format}
g = ggplot(conflict,
	   aes(seconds, value, color=Section)) +
	stat_summary(fun.data=mean_se) +
	labs(
	# labs(title="All positions - Conflict trials",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(green, red, blue)) +
	my_theme + scale_y_continuous(labels=percent) +
	theme(legend.position=c(0,1), legend.justification=c(0,1)) +
	scale_x_continuous(breaks=seq(0, 60, 5))
g
```

## All responses, no-conflict

```{r all.control, dev=fig_format, fig.width=9, fig.height=5}
g = ggplot(control,
	   aes(seconds, value, color=section)) +
	stat_summary(fun.data=mean_se) +
  labs(
	# labs(title="All positions - Control trials",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(green, blue)) +
	my_theme + scale_y_continuous(labels=percent) +
	theme(legend.position=c(0,1), legend.justification=c(0,1)) +
	scale_x_continuous(breaks=seq(0, 60, 5))
g
```


# To Chosen Response

Includes correct responsees to no-conflict trials)

Note that for computational reasons the fitted curves shown are from a model without any random effects.

```{r all.to_chosen, dev=fig_format, fig.width=9, fig.height=5}
this.data = dplyr::filter(tall.data,
						  choice=='correct' |
						  	(condition=='C' & choice=='heuristic'))
this.data = this.data[this.data$to.chosen,]
this.data$type = interaction(this.data$condition, this.data$choice) %>%
	droplevels
levels(this.data$type) = c('Correct no-conflict', 'Correct conflict',
						   'Heuristic conflict')
this.data$type %<>% factor(levels = levels(.)[c(3,1,2)])

g = this.data %>%
	ggplot(aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se) +
  labs(
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue2, green)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5))

# For plotting, fit a standard model.
# Fitted values are the same as from the multilevel model,
# but it's not tricky, and hugely time consuming, to fit a proper multilevel model
# comparing all three kinds of trial.
correct.plot.model = glm(value ~ nt1 + nt2 + nt3 + type:(nt1 + nt2 + nt3),
						 data=this.data, family=binomial)

g = g + 
  stat_summary( aes(x=seconds, y=fitted(correct.plot.model),
                    group=type, color=type),
                fun.y=mean, geom="line", size=1, alpha=.8)
```

```{r all.to_chosen.annotate, dev=fig_format, fig.width=9, fig.height=5}
g + 
  annotate('text', x=17.5, y=.775, label='Heuristic conflict',
           color=red, size=6, hjust=1) +
  annotate('text', x=28, y=.65, label='Correct no-conflict',
           color=blue2, size=6, hjust=0) +
  geom_segment(x=27.5, y=.65, xend=20.5, yend=.7,
               size = 1.2, color=black,
               arrow = arrow(length = unit(.3,"cm"))) +
  annotate('text', x=22.6, y=.525, label='Correct conflict',
           color=green, size=6, hjust=0) +
  theme(legend.position="none")
```


## Models

```{r all.to_chosen.fit,, results='asis', fig.width=9, fig.height=5}
# Next, compare Heuristic conflict, and Correct no-conflict curves
intuitive.d = filter(this.data,
					 (choice=='correct' & condition=='B') |
					 	(choice=='heuristic' & condition=='C'))
intuitive.d$type %<>% droplevels
contrasts(intuitive.d$type) = c(-.5, .5)

if(recalculate_everything | !file.exists('cache/intuitive.chosen.bias.glme.rds')){
	# Null model
	intuitive.chosen.glme0 = glmer(value ~ nt1 + nt2 + nt3 + (nt1-1|subject_nr),
								   data=intuitive.d, family=binomial,
								   control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	# Difference between curves?
	intuitive.chosen.glme1 = glmer(value ~ nt1 + nt2 + nt3 + type:(nt1+nt2+nt3) + (nt1-1|subject_nr),
								   data=intuitive.d, family=binomial,
								   control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	# Bias x Curve interaction?
	intuitive.chosen.bias.glme = glmer(value ~ nt1 + nt2 + nt3 +
											type:(nt1+nt2+nt3) + biased:type:(nt1+nt2+nt3) +
											(nt1-1|subject_nr),
										data=intuitive.d, family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Null/Difference between curves for unbiased reasoners 
	intuitive.glme.unbiased_reasoners.0 = glmer(value ~ nt1 + nt2 + nt3 + (nt1-1|subject_nr),
											  data=intuitive.d[intuitive.d$biased==F,],
											  family=binomial,
											  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	intuitive.glme.unbiased_reasoners.1 = glmer(value ~ nt1 + nt2 + nt3 + type:(nt1+nt2+nt3) + (nt1-1|subject_nr),
											  data=intuitive.d[intuitive.d$biased==F,],
											  family=binomial,
											  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

	# Null/Difference between curves for biased reasoners 
	intuitive.glme.biased_reasoners.0 = glmer(value ~ nt1 + nt2 + nt3 + (nt1-1|subject_nr),
											  data=intuitive.d[intuitive.d$biased==T,],
											  family=binomial,
											  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	intuitive.glme.biased_reasoners.1 = glmer(value ~ nt1 + nt2 + nt3 + type:(nt1+nt2+nt3) + (nt1-1|subject_nr),
											  data=intuitive.d[intuitive.d$biased==T,],
											  family=binomial,
											  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	saveRDS(intuitive.chosen.glme0, 'cache/intuitive.chosen.glme0.rds')
	saveRDS(intuitive.chosen.glme1, 'cache/intuitive.chosen.glme1.rds')
	saveRDS(intuitive.chosen.bias.glme, 'cache/intuitive.chosen.bias.glme.rds')
	saveRDS(intuitive.glme.unbiased_reasoners.0, 'cache/intuitive.glme.unbiased_reasoners.0.rds')
	saveRDS(intuitive.glme.unbiased_reasoners.1, 'cache/intuitive.glme.unbiased_reasoners.1.rds')
	saveRDS(intuitive.glme.biased_reasoners.0, 'cache/intuitive.glme.biased_reasoners.0.rds')
	saveRDS(intuitive.glme.biased_reasoners.1, 'cache/intuitive.glme.biased_reasoners.1.rds')

} else {
	intuitive.chosen.glme0 = readRDS('cache/intuitive.chosen.glme0.rds')
	intuitive.chosen.glme1 = readRDS('cache/intuitive.chosen.glme1.rds')
	intuitive.chosen.bias.glme = readRDS('cache/intuitive.chosen.bias.glme.rds')
	intuitive.glme.unbiased_reasoners.0 = readRDS('cache/intuitive.glme.unbiased_reasoners.0.rds')
	intuitive.glme.unbiased_reasoners.1 = readRDS('cache/intuitive.glme.unbiased_reasoners.1.rds')
	intuitive.glme.biased_reasoners.0 = readRDS('cache/intuitive.glme.biased_reasoners.0.rds')
	intuitive.glme.biased_reasoners.1 = readRDS('cache/intuitive.glme.biased_reasoners.1.rds')
}


anova.table(intuitive.chosen.glme0, intuitive.chosen.glme1)
coef.table(intuitive.chosen.glme1)

anova.table(intuitive.chosen.glme0, intuitive.chosen.glme1)
coef.table(intuitive.chosen.bias.glme)

anova.table(intuitive.glme.unbiased_reasoners.0, intuitive.glme.unbiased_reasoners.1)
coef.table(intuitive.glme.unbiased_reasoners.1)

anova.table(intuitive.glme.biased_reasoners.0, intuitive.glme.biased_reasoners.1)
coef.table(intuitive.glme.biased_reasoners.1)
```


```{r intuitive.to_chosen.plot, dev=fig_format, fig.width=9, fig.height=5}
intuitive.to_chosen.plot = ggplot(intuitive.d, aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se) +
	stat_summary(aes(x=seconds, y=fitted(intuitive.chosen.glme1), group=type, color=type),
				 fun.y=mean, geom="line", size=1.5, alpha=1) +
  labs(
	# labs(title="To chosen response",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue2)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5))
intuitive.to_chosen.plot
```


```{r intuitive.to_chosen.plot.byquestion, dev=fig_format, fig.width=9, fig.height=5}
intuitive.to_chosen.plot.byquestion = ggplot(
	intuitive.d,aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se, alpha=.6) +
  labs(
	# labs(title="To chosen response",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue2)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5)) +
	facet_wrap(~stimuli_number)
intuitive.to_chosen.plot.byquestion
```



```{r intuitive.to_chosen.bias.plot, dev=fig_format, fig.width=9, fig.height=9}
intuitive.to_chosen.plot.unbiased = filter(intuitive.d, biased==F) %>%
	ggplot(aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se) +
	stat_summary(aes(x=seconds, y=fitted(intuitive.glme.unbiased_reasoners.1), group=type, color=type),
				 fun.y=mean, geom="line", size=1.5, alpha=1) +
  labs(
	# labs(title="Unbiased reasoners - To chosen response",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue2)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5))

intuitive.to_chosen.plot.biased = filter(intuitive.d, biased==T) %>%
	ggplot(aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se) +
	stat_summary(aes(x=seconds, y=fitted(intuitive.glme.biased_reasoners.1), group=type, color=type),
				 fun.y=mean, geom="line", size=1.5, alpha=1) +
  labs(
	# labs(title="Biased reasoners - To chosen response",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue2)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5))

gridExtra::grid.arrange(intuitive.to_chosen.plot.unbiased,
                        intuitive.to_chosen.plot.biased, ncol=1)

```


```{r}
rm(intuitive.chosen.glme0)
rm(intuitive.chosen.glme1)
rm(intuitive.chosen.bias.glme)
rm(intuitive.glme.unbiased_reasoners.0)
rm(intuitive.glme.unbiased_reasoners.1)
rm(intuitive.glme.biased_reasoners.0)
rm(intuitive.glme.biased_reasoners.1)
```

## To Chosen Response (conflict)

```{r conflict.to_chosen, dev=fig_format, fig.width=9, fig.height=5}
conflict.d = filter(this.data, condition=='C' & choice!='other')
conflict.d$section %<>% droplevels
conflict.d$Section = conflict.d$section
levels(conflict.d$Section) = c('Correct conflict', 'Heuristic conflict')

contrasts(conflict.d$Section) = c(-.5, .5)

# g = conflict.d %>%
# 	ggplot(aes(seconds, value, color=Section)) +
# 	stat_summary(fun.data=mean_se) +
# 	labs(title="To chosen response - Conflict condition",
# 		 x="Seconds", y="Proportion of trials", colour="Response region") + 
# 	theme_bw() +
# 	scale_color_manual(values=c(green, red, blue)) +
# 	my_theme + scale_y_continuous(labels=percent) +
# 	scale_x_continuous(breaks=seq(0, 60, 5)) +
# 	theme(legend.position=c(1,0), legend.justification=c(1,0))
# g
```


```{r conflict.to_chosen.fit, results='asis', fig.width=9, fig.height=5}
if(recalculate_everything | !file.exists('cache/conflict.chosen.bias.glme.rds')){
	# Null
	conflict.chosen.glme0 = glmer(value ~ nt1 + nt2 + nt3 + (nt1-1|subject_nr),
								  data=conflict.d, family=binomial,
								  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves?
	conflict.chosen.glme1 = glmer(value ~ nt1 + nt2 + nt3 + section:(nt1+nt2+nt3) + (nt1-1|subject_nr),
								  data=conflict.d, family=binomial,
								  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Bias x Curve interaction?
	conflict.chosen.bias.glme = glmer(value ~ nt1 + nt2 + nt3 +
									  	section:(nt1+nt2+nt3) + biased:section:(nt1+nt2+nt3) +
									  	(nt1-1|subject_nr),
									  data=conflict.d, family=binomial,
									  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Null/Difference between curves for unbiased reasoners 
	conflict.glme.unbiased_reasoners.0 = glmer(value ~ nt1 + nt2 + nt3 + (nt1-1|subject_nr),
											   data=conflict.d[conflict.d$biased==F,],
											   family=binomial,
											   control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	conflict.glme.unbiased_reasoners.1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) + (nt1-1|subject_nr),
											   data=conflict.d[conflict.d$biased==F,],
											   family=binomial,
											   control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

	# Null/Difference between curves for biased reasoners 
	conflict.glme.biased_reasoners.0 = glmer(value ~ nt1 + nt2 + nt3 + (nt1-1|subject_nr),
											  data=conflict.d[conflict.d$biased==T,],
											  family=binomial,
											  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	conflict.glme.biased_reasoners.1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) + (nt1-1|subject_nr),
											  data=conflict.d[conflict.d$biased==T,],
											  family=binomial,
											  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	saveRDS(conflict.chosen.glme0, 'cache/conflict.chosen.glme0.rds')
	saveRDS(conflict.chosen.glme1, 'cache/conflict.chosen.glme1.rds')
	saveRDS(conflict.chosen.bias.glme, 'cache/conflict.chosen.bias.glme.rds')
	saveRDS(conflict.glme.unbiased_reasoners.0, 'cache/conflict.glme.unbiased_reasoners.0.rds')
	saveRDS(conflict.glme.unbiased_reasoners.1, 'cache/conflict.glme.unbiased_reasoners.1.rds')
	saveRDS(conflict.glme.biased_reasoners.0, 'cache/conflict.glme.biased_reasoners.0.rds')
	saveRDS(conflict.glme.biased_reasoners.1, 'cache/conflict.glme.biased_reasoners.1.rds')
} else {
	conflict.chosen.glme0 = readRDS('cache/conflict.chosen.glme0.rds')
	conflict.chosen.glme1 = readRDS('cache/conflict.chosen.glme1.rds')
	conflict.chosen.bias.glme = readRDS('cache/conflict.chosen.bias.glme.rds')
	conflict.glme.unbiased_reasoners.0 = readRDS('cache/conflict.glme.unbiased_reasoners.0.rds')
	conflict.glme.unbiased_reasoners.1 = readRDS('cache/conflict.glme.unbiased_reasoners.1.rds')
	conflict.glme.biased_reasoners.0 = readRDS('cache/conflict.glme.biased_reasoners.0.rds')
	conflict.glme.biased_reasoners.1 = readRDS('cache/conflict.glme.biased_reasoners.1.rds')

}
anova.table(conflict.chosen.glme0, conflict.chosen.glme1)
coef.table(conflict.chosen.glme1)

anova.table(conflict.chosen.glme0, conflict.chosen.glme1)
coef.table(conflict.chosen.bias.glme)


anova.table(conflict.glme.unbiased_reasoners.0, conflict.glme.unbiased_reasoners.1)
coef.table(conflict.glme.unbiased_reasoners.1)

anova.table(conflict.glme.biased_reasoners.0, conflict.glme.biased_reasoners.1)
coef.table(conflict.glme.biased_reasoners.1)
```


```{r conflict.to_chosen.plot, dev=fig_format, fig.width=9, fig.height=5}
conflict.to_chosen.plot = ggplot(conflict.d, aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se) +
	stat_summary(aes(x=seconds, y=fitted(conflict.chosen.glme1), group=type, color=type),
				 fun.y=mean, geom="line", size=1.5, alpha=1) +
	labs(
  # labs(title="Unbiased reasoners - To chosen response",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, green)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5))
conflict.to_chosen.plot
```


```{r conflict.to_chosen.bias.plot, dev=fig_format, fig.width=9, fig.height=9}
conflict.to_chosen.plot.unbiased = filter(conflict.d, biased==F) %>%
	ggplot(aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se) +
	stat_summary(aes(x=seconds, y=fitted(conflict.glme.unbiased_reasoners.1), group=type, color=type),
				 fun.y=mean, geom="line", size=1.5, alpha=1) +
  labs(
	# labs(title="Unbiased reasoners - To chosen response",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, green)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5))

conflict.to_chosen.plot.biased = filter(conflict.d, biased==T) %>%
	ggplot(aes(seconds, value, color=type)) +
	stat_summary(fun.data=mean_se) +
	stat_summary(aes(x=seconds, y=fitted(conflict.glme.biased_reasoners.1), group=type, color=type),
				 fun.y=mean, geom="line", size=1.5, alpha=1) +
	labs(title="Biased reasoners - To chosen response",
		 x="Seconds", y="Proportion of trials", colour="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, green)) +
	my_theme + scale_y_continuous(labels=percent, breaks=seq(.25, 1.01, .25)) +
	theme(legend.position=c(1,0), legend.justification=c(1,0)) +
	scale_x_continuous(breaks=seq(0, 60, 5))

gridExtra::grid.arrange(conflict.to_chosen.plot.unbiased,
                        conflict.to_chosen.plot.biased, ncol=1)
```

```{r}
rm(conflict.chosen.glme0)
rm(conflict.chosen.glme1)
rm(conflict.chosen.bias.glme)
rm(conflict.glme.unbiased_reasoners.0)
rm(conflict.glme.unbiased_reasoners.1)
rm(conflict.glme.biased_reasoners.0)
rm(conflict.glme.biased_reasoners.1)
```


# To non-chosen response
	
```{r dev=fig_format, fig.width=9, fig.height=9}
not.chosen = conflict[conflict$to.chosen==F,]
not.chosen = not.chosen[not.chosen$choice!='other',]
 
correct.choices = not.chosen[not.chosen$choice=='correct',]
# not.chosen %>%
# 	ggplot(aes(seconds, value, color=Section)) +
# 	stat_summary(fun.data=mean_se) +
# 	facet_wrap(~choice, ncol=1) +
# 	labs(title="Mouse cursor placement over time",
# 		 x="Seconds", y="Proportion of trials", color="Response\nregion") + 
# 	theme_bw() +
# 	scale_color_manual(values=c(green, red, blue)) +
# 	scale_y_continuous(labels=percent) +
# 	scale_x_continuous(breaks=seq(0, 60, 5)) +
# 	my_theme + theme(legend.position=c(1,1), legend.justification=c(1,1))
```

## Correct choices

## model

```{r correct.not_chosen.fit, dev=fig_format, results='asis'}
# contrasts(correct.choices$Section)
if(recalculate_everything | !file.exists('cache/notchosen.correct.bias.glme1.rds')){
	# Null model
	notchosen.correct.glme0 = glmer(value ~ nt1 + nt2 + nt3 +
										(nt1-1|subject_nr),
			  data=correct.choices, family=binomial,
			  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves
	notchosen.correct.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
			  data=correct.choices, family=binomial,
			  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Interaction with participants' bias?
	notchosen.correct.bias.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										biased:Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
			  data=correct.choices, family=binomial,
			  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves for UNBIASED reasoners
	# Null model
	notchosen.correct.unbiased.glme0 = glmer(value ~ nt1 + nt2 + nt3 +
										(nt1-1|subject_nr),
										data=correct.choices[correct.choices$biased==F,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves
	notchosen.correct.unbiased.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
										data=correct.choices[correct.choices$biased==F,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

	
	# Difference between curves for BIASED reasoners
	# Null model
	notchosen.correct.biased.glme0 = glmer(value ~ nt1 + nt2 + nt3 +
										(nt1-1|subject_nr),
										data=correct.choices[correct.choices$biased==T,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves
	notchosen.correct.biased.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
										data=correct.choices[correct.choices$biased==T,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

	
	
	
	saveRDS(notchosen.correct.glme0,
	        'notchosen.correct.glme0.rds')
	saveRDS(notchosen.correct.glme1,
	        'notchosen.correct.glme1.rds')
	saveRDS(notchosen.correct.bias.glme1, 'cache/notchosen.correct.bias.glme1.rds')
	saveRDS(notchosen.correct.unbiased.glme0, 'cache/notchosen.correct.unbiased.glme0.rds')
	saveRDS(notchosen.correct.unbiased.glme1, 'cache/notchosen.correct.unbiased.glme1.rds')
	saveRDS(notchosen.correct.biased.glme0, 'cache/notchosen.correct.biased.glme0.rds')
	saveRDS(notchosen.correct.biased.glme1, 'cache/notchosen.correct.biased.glme1.rds')
} else {
	notchosen.correct.glme0 = readRDS('cache/notchosen.correct.glme0.rds')
	notchosen.correct.glme1 = readRDS('cache/notchosen.correct.glme1.rds')
	notchosen.correct.bias.glme1 = readRDS('cache/notchosen.correct.bias.glme1.rds')
	notchosen.correct.unbiased.glme0 = readRDS('cache/notchosen.correct.unbiased.glme0.rds')
	notchosen.correct.unbiased.glme1 = readRDS('cache/notchosen.correct.unbiased.glme1.rds')
	notchosen.correct.biased.glme0 = readRDS('cache/notchosen.correct.biased.glme0.rds')
	notchosen.correct.biased.glme1 = readRDS('cache/notchosen.correct.biased.glme1.rds')
}

# Sig. diff between the lines
anova.table(notchosen.correct.glme0, notchosen.correct.glme1)
# Sig. diff on time, time^2, and time^3
coef.table(notchosen.correct.glme1)

# Significant bias x curve interaction
anova.table(notchosen.correct.glme1, notchosen.correct.bias.glme1)
# No chance of interpreting these coefficients
coef.table(notchosen.correct.bias.glme1)

# UNBIASED reasoners
# (basically the same story as the main effect)
# Sig. diff between the lines
anova.table(notchosen.correct.unbiased.glme0, notchosen.correct.unbiased.glme1)
# Sig. diff on time, time^2, and time^3
coef.table(notchosen.correct.unbiased.glme1)

# BIASED reasoners
# (rarely make correct responses, so messier data)
# Sig. diff between the lines
anova.table(notchosen.correct.biased.glme0, notchosen.correct.biased.glme1)
# Sig. diff on time, time^2, and time^3
coef.table(notchosen.correct.biased.glme1)
```

```{r correct.not_chosen.plot, dev=fig_format, fig.width=9, fig.height=5}
correct.not_chosen.plot = ggplot(correct.choices,
				   aes(seconds, value, color=Section)) +
	stat_summary(fun.data=mean_se) +
  labs(
	# labs(title="To non-chosen response\n(when chosing correct one)",
		 x="Seconds", y="Proportion of trials", color="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue)) +
	scale_y_continuous(labels=percent) +
	scale_x_continuous(breaks=seq(0, 60, 5)) +
	theme(legend.position=c(1,1), legend.justification=c(1,1)) +
	my_theme +
  stat_summary(aes(x=seconds, y=fitted(notchosen.correct.glme1), color=Section),
               fun.y=mean, geom="line", size=1.5, alpha=1)
correct.not_chosen.plot  
```

```{r correct.not_chosen.plot.annotate, dev=fig_format, fig.width=9, fig.height=5}
correct.not_chosen.plot + 
  annotate('text', x=39, y=.09, label='Heuristic option',
           color=red, size=6, hjust=0, angle=0) +
  annotate('text', x=28, y=.045, label='Correct option',
           color=blue, size=6, hjust=1, angle=0) +
  theme(legend.position="none")
```



```{r correct.not_chosen.biased.plot, dev=fig_format, fig.width=9, fig.height=9}
correct.not_chosen.plot.unbiased = ggplot(correct.choices[correct.choices$biased==F,],
					aes(seconds, value, color=Section)) +
	stat_summary(fun.data=mean_se) +
  labs(
	# labs(title="Unbiased reasoners",
		 x="Seconds", y="Proportion of trials", color="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue)) +
	theme(legend.position=c(1,1), legend.justification=c(1,1)) +
	scale_y_continuous(labels=percent) +
	scale_x_continuous(breaks=seq(0, 60, 5)) + my_theme +
	stat_summary(aes(x=seconds, y=fitted(notchosen.correct.unbiased.glme1), color=Section),
				 fun.y=mean, geom="line", size=1.5, alpha=1)

correct.not_chosen.plot.biased = ggplot(correct.choices[correct.choices$biased==T,],
					aes(seconds, value, color=Section)) +
	stat_summary(fun.data=mean_se) +
  labs(
	# labs(title="Biased reasoners",
		 x="Seconds", y="Proportion of trials", color="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(red, blue)) +
	theme(legend.position=c(1,1), legend.justification=c(1,1)) +
	scale_y_continuous(labels=percent) +
	scale_x_continuous(breaks=seq(0, 60, 5)) + my_theme +
	stat_summary(aes(x=seconds, y=fitted(notchosen.correct.biased.glme1), color=Section),
				 fun.y=mean, geom="line", size=1.5, alpha=1) + guides(color=FALSE)

gridExtra::grid.arrange(correct.not_chosen.plot.unbiased,
                        correct.not_chosen.plot.biased, ncol=1)

```

```{r}
rm(notchosen.correct.glme0)
rm(notchosen.correct.glme1)
rm(notchosen.correct.bias.glme1)
rm(notchosen.correct.unbiased.glme0)
rm(notchosen.correct.unbiased.glme1)
rm(notchosen.correct.biased.glme0)
rm(notchosen.correct.biased.glme1)
```

## Heuristic choices

```{r heuristic.not_chosen, dev=fig_format, fig.width=9, fig.height=5}
heuristic.choices = not.chosen[not.chosen$choice=='heuristic',]
```

```{r heuristic.not_chosen.biasedA, dev=fig_format, fig.width=9, fig.height=9}
# heuristic.g + facet_wrap(~biased)
```

```{r, results='asis'}
# contrasts(correct.choices$Section)
if(recalculate_everything | !file.exists('cache/notchosen.heuristic.bias.glme1.rds')){
	# Null model
	notchosen.heuristic.glme0 = glmer(value ~ nt1 + nt2 + nt3 +
										(nt1-1|subject_nr),
			  data=heuristic.choices, family=binomial,
			  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves
	notchosen.heuristic.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
			  data=heuristic.choices, family=binomial,
			  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Interaction with participants' bias?
	notchosen.heuristic.bias.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										biased:Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
			  data=heuristic.choices, family=binomial,
			  control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

	
	# Difference between curves for UNBIASED reasoners
	# Null model
	notchosen.heuristic.unbiased.glme0 = glmer(value ~ nt1 + nt2 + nt3 +
										(nt1-1|subject_nr),
										data=heuristic.choices[heuristic.choices$biased==F,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves
	notchosen.heuristic.unbiased.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
										data=heuristic.choices[heuristic.choices$biased==F,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

	
	# Difference between curves for BIASED reasoners
	# Null model
	notchosen.heuristic.biased.glme0 = glmer(value ~ nt1 + nt2 + nt3 +
										(nt1-1|subject_nr),
										data=heuristic.choices[heuristic.choices$biased==T,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))
	
	# Difference between curves
	notchosen.heuristic.biased.glme1 = glmer(value ~ nt1 + nt2 + nt3 + Section:(nt1+nt2+nt3) +
										(nt1-1|subject_nr),
										data=heuristic.choices[heuristic.choices$biased==T,], family=binomial,
										control = glmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))	
	
	
	saveRDS(notchosen.heuristic.glme0, 'cache/notchosen.heuristic.glme0.rds')
	saveRDS(notchosen.heuristic.glme1, 'cache/notchosen.heuristic.glme1.rds')
	saveRDS(notchosen.heuristic.bias.glme1, 'cache/notchosen.heuristic.bias.glme1.rds')
	saveRDS(notchosen.heuristic.unbiased.glme0, 'cache/notchosen.heuristic.unbiased.glme0.rds')
	saveRDS(notchosen.heuristic.unbiased.glme1, 'cache/notchosen.heuristic.unbiased.glme1.rds')
	saveRDS(notchosen.heuristic.biased.glme0, 'cache/notchosen.heuristic.biased.glme0.rds')
	saveRDS(notchosen.heuristic.biased.glme1, 'cache/notchosen.heuristic.biased.glme1.rds')
} else {
	notchosen.heuristic.glme0 = readRDS('cache/notchosen.heuristic.glme0.rds')
	notchosen.heuristic.glme1 = readRDS('cache/notchosen.heuristic.glme1.rds')
	notchosen.heuristic.bias.glme1 = readRDS('cache/notchosen.heuristic.bias.glme1.rds')
	notchosen.heuristic.unbiased.glme0 = readRDS('cache/notchosen.heuristic.unbiased.glme0.rds')
	notchosen.heuristic.unbiased.glme1 = readRDS('cache/notchosen.heuristic.unbiased.glme1.rds')
	notchosen.heuristic.biased.glme0 = readRDS('cache/notchosen.heuristic.biased.glme0.rds')
	notchosen.heuristic.biased.glme1 = readRDS('cache/notchosen.heuristic.biased.glme1.rds')
}
	
# Difference between the curves	
anova.table(notchosen.heuristic.glme0, notchosen.heuristic.glme1)
# Sig. on every term
coef.table(notchosen.heuristic.glme1)

# Bias by curve interaction
anova.table(notchosen.heuristic.glme1, notchosen.heuristic.bias.glme1)
# Sig on lots of terms, but uninterpretable
coef.table(notchosen.heuristic.bias.glme1)


# UNBIASED reasoners
# (basically the same story as the main effect)
# Sig. diff between the lines
anova.table(notchosen.heuristic.unbiased.glme0, notchosen.heuristic.unbiased.glme1)
# Sig. diff on time, time^2, and time^3
coef.table(notchosen.heuristic.unbiased.glme1)

# BIASED reasoners
# (rarely make heuristic responses, so messier data)
# Sig. diff between the lines
anova.table(notchosen.heuristic.biased.glme0, notchosen.heuristic.biased.glme1)
# Sig. diff on time, time^2, and time^3
coef.table(notchosen.heuristic.biased.glme1)
```

```{r heuristic.not_chosen.plot, dev=fig_format, fig.width=9, fig.height=5}
heuristic.not_chosen.plot = ggplot(heuristic.choices,
					 aes(seconds, value, color=Section)) +
	stat_summary(fun.data=mean_se) +
  labs(
	# labs(title="To non-chosen response\n(when chosing heuristic one)",
		 x="Seconds", y="Proportion of trials", color="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(green, blue)) +
	theme(legend.position=c(1,1), legend.justification=c(1,1)) +
	my_theme + scale_y_continuous(labels=percent) + 
  stat_summary(aes(x=seconds, y=fitted(notchosen.heuristic.glme1), color=Section),
               fun.y=mean, geom="line", size=1.5, alpha=1)
heuristic.not_chosen.plot
```

```{r heuristic.not_chosen.plot.annotate, dev=fig_format, fig.width=9, fig.height=5}
heuristic.not_chosen.plot + 
  annotate('text', x=13, y=.175, label='Foil option',
           color=blue, size=6, hjust=0, angle=0) +
  annotate('text', x=12, y=.09, label='Correct option',
           color=green, size=6, hjust=1, angle=0) +
  theme(legend.position="none")
```




```{r heuristic.not_chosen.biased.plot, dev=fig_format, fig.width=9, fig.height=9}
heuristic.not_chosen.plot.unbiased = ggplot(heuristic.choices[heuristic.choices$biased==F,],
					aes(seconds, value, color=Section)) +
	stat_summary(fun.data=mean_se) +
  labs(
	# labs(title="Unbiased reasoners",
		 x="Seconds", y="Proportion of trials", color="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(green, blue)) +
	theme(legend.position=c(1,1), legend.justification=c(1,1)) +
	scale_y_continuous(labels=percent) +
	scale_x_continuous(breaks=seq(0, 60, 5)) + my_theme +
	stat_summary(aes(x=seconds, y=fitted(notchosen.heuristic.unbiased.glme1), color=Section),
				 fun.y=mean, geom="line", size=1.5, alpha=1)

heuristic.not_chosen.plot.biased = ggplot(heuristic.choices[heuristic.choices$biased==T,],
					aes(seconds, value, color=Section)) +
	stat_summary(fun.data=mean_se) +
  labs(
	# labs(title="Biased reasoners",
		 x="Seconds", y="Proportion of trials", color="Response region") + 
	theme_bw() +
	scale_color_manual(values=c(green, blue)) +
	theme(legend.position=c(1,1), legend.justification=c(1,1)) +
	scale_y_continuous(labels=percent) +
	scale_x_continuous(breaks=seq(0, 60, 5)) + my_theme +
	stat_summary(aes(x=seconds, y=fitted(notchosen.heuristic.biased.glme1), color=Section),
				 fun.y=mean, geom="line", size=1.5, alpha=1) + guides(color=FALSE)

gridExtra::grid.arrange(heuristic.not_chosen.plot.unbiased,
                        heuristic.not_chosen.plot.biased, ncol=1)
```


```{r}
rm(notchosen.heuristic.glme0)
rm(notchosen.heuristic.glme1)
rm(notchosen.heuristic.bias.glme1)
rm(notchosen.heuristic.unbiased.glme0)
rm(notchosen.heuristic.unbiased.glme1)
rm(notchosen.heuristic.biased.glme0)
rm(notchosen.heuristic.biased.glme1)
```
